### 2019-07-24 thesis.tex
* thesis.tex: Summary: new paragraph

The analysis presented in this doctoral thesis has relevant contributions in the
study of the combined action of nonlinear kinetic instabilities and collisional
processes in unmagnetized, fully ionized, hydrogen plasmas. Though the plasma's
profile under consideration might be considered quite idealized, the physical
processes that are being addressed have fundamental character - the plasma waves
under consideration and the particle interactions are inherent to any plasma.
The underlying nature of these processes means that they might impact the plasma
dynamics at different astrophysical environments and also in laboratory plasmas.
Laboratory plasmas, however, are usually constrained by very specific conditions
that are unique to each experiment. This specificity makes the analysis in the
experimental context counter productive. A more broad approach is to compare our
theoretical results with plasma phenomena that are independent of imposed laboratory
conditions: astrophysical plasmas.

 In this appendix, we will make a brief revision on solar
physics, pointing out the phenomena that are associated with our model.

>>>>

The analysis presented in this doctoral thesis has relevant contributions in the
study of the combined action of nonlinear kinetic instabilities and collisional
processes in unmagnetized, fully ionized, hydrogen plasmas. Though the plasma's
profile under consideration might be considered quite idealized, the physical
processes that are being addressed have fundamental character - the plasma waves
under consideration and the particle interactions are inherent to any plasma.
The underlying nature of these processes means that they might impact the plasma
dynamics at different astrophysical environments and also in laboratory plasmas.
Laboratory plasmas, however, are usually constrained by very specific conditions
that are unique to each experiment. This specificity makes the analysis in the
experimental context counter productive. A more broad approach was then to compare
our theoretical results with phenomena observed in the naturally occurring space
plasma.

Astrophysical plasmas are observed in a vast range of densities, temperatures,
magnetic fields, and scale lengths\footnote{The description of such an extensive list is
out of the scope of this text. On that matter, Ref.~\cite{peratt2014} offers a
quite complete description of space plasma and space plasma phenomena occurring
in all cosmic scales.}.  
 In this appendix, we will make a brief revision on solar
physics, pointing out the phenomena that are associated with our model.
